### 2020-11-16 doc/manuscript/Dow_manuscript.Rmd
DOY_gmax --> DOY_ip

For both ring- and diffuse- porous species at both sites, warmer spring temperatures resulted in earlier achievement of growth milestones (Tables `r hypothesis_table`, Figs. `r pheno_Tsensitivity`, `r DOYtiming`).
Specifically, $DOY_{25}$, $DOY_{50}$, $DOY_{75}$, and $DOY_{g.max}$ all decreased significantly with increasing $T_{max}$ during the critical period (Table `r mean_growth_parameters_table`).

>>>>

For both ring- and diffuse- porous species at both sites, warmer spring temperatures resulted in earlier achievement of growth milestones (Tables `r hypothesis_table`, Figs. `r pheno_Tsensitivity`, `r DOYtiming`).
Specifically, $DOY_{25}$, $DOY_{50}$, $DOY_{75}$, and $DOY_{ip}$ all decreased significantly with increasing $T_{max}$ during the critical period (Table `r mean_growth_parameters_table`).
